### 2020-05-31 writeup/setup.tex
sec 2

Recall that we have $t$ labeled tasks as the training dataset, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
%Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d. entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
Without loss of generality, let the $t$-th task denote the target task.
We consider a linear multi-task learning architecture by minimizing the following
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2,
\end{align}
where $B\in\real^{p\times r}$ and $W_i\in\real^r$.
Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ to be the single-task optimum.
Hence there is no positive or negative transfer.
We define $\hat{\beta}_t^{\MTL}$ by two steps:
(i) minimizing $f(\cdot)$ over $B$;
(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set.
For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample (prediction) loss as
	\begin{align*}
		\te_t(\hat{\beta}) \define \exarg{z}{\exarg{\varepsilon_t}{({(\Sigma_t^{1/2} z)}^{\top}\hat{\beta} - {(\Sigma_t^{1/2})}^{\top}\beta_t)^2}}
		= \exarg{\varepsilon_t}{(\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t)}.
	\end{align*}
The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
The bias-variance trade-off \cite{HTF09} says
	\[ \te_t(\hat{\beta}) =
		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\bignorm{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}^2}. \]
In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
%Recall that $n_i = \rho_i \cdot p$ and we assume $\rho_i > 1$ is a fixed constant for every $1\le i\le t$.

@@

\textbf{Notations.}
When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
We refer to the first task as the source task when there are only two tasks.
We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.

@@

To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts (to be derived in Appendix \ref{app_proof_sec3}) as follows
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
\end{align}
where $\hat{v} = W_2 / W_1$ denotes the ratio of the output layer weights.
The scaling term $\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
The output layer of each task scales the direction of $B$ suitably to fit the task.

>>>>

Recall that we have $t$ labeled tasks as the training dataset, denoted by $(X_1, Y_1), (X_2, Y_2), \dots, (X_t, Y_t)$, where $X_i\in\real^{n_i\times p}$ and $Y_i\in\real^{n_i}$ for $1\le i\le t$.
%Following \cite{HMRT19,BLLT20}, we assume that for each task $i = 1,2,\dots,t$,  every feature vector is generated as $x = \Sigma_i^{1/2} z$, where $z\in\real^p$ is a random vector with i.i.d. entries of mean zero and unit variance and $\Sigma_i\in\real^{p\times p}$ is a positive semidefinite matrix.
Without loss of generality, let the $t$-th task denote the target task.
We consider a linear multi-task learning architecture by minimizing the following
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_t) = \sum_{i=1}^t \norm{X_i B W_i - Y_i}^2,
\end{align}
where $B\in\real^{p\times r}$ and $W_i\in\real^r$.
Here $B$ provides a shared subspace for all tasks and $W_i$ fits $B$ suitably to each task.
Following \cite{WZR20}, we assume that $r < t$, because otherwise minimizing $f(\cdot)$ could result in $BW_i$ to be the single-task optimum.
Hence there is no positive or negative transfer.
We define $\hat{\beta}_t^{\MTL}$ by two steps:
(i) minimizing $f(\cdot)$ over $B$;
(ii) minimize $\set{W_i}_{i=1}^k$ over an independent sample of the training set.
For more details, we refer the reader to Appendix \ref{app_proof_sec3}.
For an estimator $\hat{\beta}\in\real^p$, we define the out-of-sample (prediction) loss as
	\begin{align*}
		\te_t(\hat{\beta}) \define \exarg{x}{({x}^{\top}\hat{\beta} - {x}^{\top}\beta_t)^2}
		= (\hat{\beta} - \beta_t)^{\top}\Sigma_t(\hat{\beta} - \beta_t).
	\end{align*}
The single-task estimator $\hat{\beta}_t^{\STL}$ is given by $(X_t^{\top}X_t)^{-1}X_t^{\top}Y_t$.
The bias-variance trade-off \cite{HTF09} says
	\[ \te_t(\hat{\beta}) =
		\bignorm{\exarg{\varepsilon_t}{\hat{\beta}} - \beta_t}^2 + \exarg{\varepsilon_t}{\bignorm{\hat{\beta} - \exarg{\varepsilon_t}{\hat{\beta}}}^2}. \]
In order to study the trade-off between model-shift bias and variance reduction, we need tight concentration bounds to quantify both effects.
For this purpose, we consider the high-dimensional regime where $n_i$ is a fixed constant $\rho_i > 1$ times $p$ for every $1\le i\le t$, and $p$ is large.
%Recall that $n_i = \rho_i \cdot p$ and we assume $\rho_i > 1$ is a fixed constant for every $1\le i\le t$.

@@

\textbf{Notations.}
When there is no ambiguity, we drop the subscript $t$ from $\te_t(\hat{\beta}_t^{\MTL})$ to $\te(\hat{\beta}_t^{\MTL})$ for simplicity.
We refer to the first task as the source task when there are only two tasks.
%We call $M = \Sigma_1^{1/2}\Sigma_2^{-1/2}$ the covariate shift matrix.

@@

To illustrate our intuition, we begin by considering the setting of two tasks with general covariance matrices.
%Recall that $\hat{\beta}_t^{\MTL}$ is defined as $BW_t$ after solving equation \eqref{eq_mtl}.
We decompose the test error of $\hat{\beta}_{t}^{\MTL}$ on the target task into two parts as follows.
\begin{align}
	\te(\hat{\beta}_t^{\MTL}) =& ~ \hat{v}^2 \bignorm{\Sigma_2^{1/2} (\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1 (\beta_1 - \hat{v}\beta_2)}^2 \label{eq_te_model_shift} \\
	&+ \sigma^2\cdot \bigtr{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}, \label{eq_te_var}
\end{align}
Here $\hat{v}$ denotes a fixed value that depends on the output layer weights.
$\hat{v}$ corresponds to the intuition that the shared module $B$ learns a subspace for both tasks.
These are derived in Appendix \ref{app_proof_sec3}.
